### 2021-01-24 paper/intro.tex
First draft of Sec 1.3

>>>>

\subsection{Contributions}

This paper is the first model of relaxed memory with a compositional
semantics for sequential composition.  It shows how the pomsets with
preconditions model of~\cite{DBLP:journals/pacmpl/JagadeesanJR20} can be combined
with the predicate transformer model of~\cite{???}.
\begin{itemize}
\item \S\ref{sec:model} presents the basic model, with few features
  required of the logic of preconditions, but a resulting laack of fidelity
  to exiting models,
\item \S\ref{sec:q} adds a model of \emph{quiescence} to the logic,
  required to model coherence (accessing $x$ has a precondition that $x$ is quiescent)
  and synchronization (a releasing write requires all locations to be quiescent),
\item \S\ref{sec:arm} adds the features required for efficient compilation
  to modern architectures: downgrading some synchronized accesses to relaxed,
  and removing read-read dependencies,
\item \S\ref{sec:complications} show how to address common litmus tests, and
\item \S\ref{sec:discussion} is a discussion of the design space.
\end{itemize}
% Acknowledgements go here, once we're not double-blinded.
